---
output: github_document
---

# blopmatch: Matching Estimator based on a Bilevel Optimization Problem

An implementation of Díaz, Rau and Rivera (2015) matching estimator for causal inference.
  The authors propose a matching estimator based on a Bilevel Optimization Problem. In raw terms,
  the two problems are (1) finding a convex combination that (2) using the closets neighbors possible.
  The solution to this problem allows computing Treatment Effect estimators that significantly improve
  balance in case-control studies, and furthermore, can be used for data imputation.

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Installation

```r
devtools::install_github("gvegayon/blopmatch")
```

## Examples

```{r}
# Loading the package
library(blopmatch)

# Simulating data
set.seed(1331)
X <- matrix(rnorm(20*2), ncol=2)

# Matching individual 5 to the rest
ans <- blopi_glpk(5, X)

# Resulting weights (matches)
ans$lambda

# Target vs Projected
X[5,]
colSums(ans$lambda*X[-5,])
```

